---
title: "Exercises for class 1"
output: html_document
date: "13-02-24"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Exercises for Class 1

## Supporting code

Below is code from Chapter 2 of the book that you can use to do the exercises. Not all the code you require is here though. Make sure to not rush it and take time to play around with each function. :))

```{r}
# Grid Approximation

# define grid
p_grid = seq(from = 0, to = 1, length.out=20)

# define prior
prior = rep(1, 20)

# compute likelihood at each value in grid
likelihood = dbinom(6, size = 9, prob = p_grid)

# compute product of likelihood and prior
unstd.posterior = likelihood * prior

# standardize the posterior so it sums to 1
posterior = unstd.posterior / sum(unstd.posterior)

# plot the distribution
plot(p_grid, posterior, type = "b",
     xlab = "probability of water", ylab = "posterior_probability")
mtext("20 points")

```

## Exercises

### Easy

2E1. 

```{r}
#(2) pr(rain|monday)
```

2E2.

```{r}

# (3) The probability that it is monday gives that is raining.

```

2E3.

```{r}

# (1) pr(Monday|rain)

```

2E4.

```{r}

# Probability is uncertainity, so saying the the probability of water is 0.7, is basically just our best guess. 

```

### Medium

2M1.

```{r}
# (1) YASSS
likelihood = dbinom(3, size = 3, prob = 0.7) # your own belief vs what actually happens

# (2) YASSS
likelihood = dbinom(3, size = 4, prob = 0.7)

# (3) YASSS
likelihood = dbinom(5, size = 7, prob = 0.7)
print(paste("Yasss the likelihood is",likelihood, "slayyy"))
```
## (1) The likelihood basically means, that there is 34% probability of getting water three out of three times. 
## (2) The likelihood basically means, that there is 41% probability of getting water three out of four times. 
## (3) The likelihood basically means, that there is 31% probability of getting water five out of seven times. 

2M2.

```{r}
# In the book, McElreath says that we can do much better than choosing a uniform prior for estimating the coverage of water. Is this what we are doing here? How does that impact our estimation?

# define grid
p_grid = seq(from = 0, to = 1, length.out=20)

# define prior
prior = c(rep(0,10),rep(1,10)) 


# compute likelihood at each value in grid
likelihood = dbinom(3, size = 3, prob = 0.7)

# compute product of likelihood and prior
unstd.posterior = likelihood * prior

# standardize the posterior so it sums to 1
posterior = unstd.posterior / sum(unstd.posterior)

# plot the distribution
plot(p_grid, posterior, type = "b",
     xlab = "probability of water", ylab = "posterior_probability")
mtext("20 points")
```

2M3.

```{r}
# Use the Bayes formula!
bayesTheorem <- function(pA, pB, pBA) {
  pAB <- pA * pBA / pB
  return(pAB)
}


## Doneeeee
PrEarth <- 0.5
PrLandEarth <- 0.3
PrLand <- 0.65

## We did it 
bayesTheorem(PrEarth, PrLand, PrLandEarth)
```

For the exercises below, I highly suggest you to grab a piece of paper and try to solve the problems in a 'visual' way.

2M4.

```{r}

# Write your probability here.

```

2M5.

```{r}

# Write your probability here.

```

2M6.

```{r}

# Write your probability here.

```
